---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```



1. Read in `districts.csv` into a tibble named `districts`.

```{r}
districts <- read_csv("../data/districts.csv")
```

```{r}
districts
```

2. Notice that the first row corresponds to the whole State of Tennessee. Remove this row and save the result back to `districts`.


```{r}
districts <- districts[-c(1), ]
districts
```

3. How many districts have a proficiency rate of at least 80% for both alg_1 and eng_1?



```{r}
districts |> 
  filter(alg_1>=80 & eng_1>=80 ) |> 
  count(system_name) |> 
  summarise(total_districts = n())
```
4. How many districts have a proviciency rate less than 50% for either alg_1 or eng_1?


```{r}
districts |> 
  filter(alg_1<50 | eng_1<50) |> 
  count(system_name) |> 
  summarise(total_districts = n())
```


5. Which district has the lowest graduation rate?


```{r}
districts |>
  select(system_name, grad) |> 
  arrange(grad) |> 
  slice_head(n=1)
```
6. Within the Mid Cumberland region, which district has the highest ACT composite?


```{r}
districts |> 
  filter(region == c('Mid Cumberland')) |>
  select(system_name, act_composite) |> 
  arrange(desc(act_composite)) |> 
  slice_head(n=1)
  

```
7. Create a scatter plot to compare alg_1 proficiency rates to alg_2 rates. What do you notice? Facet this plot by region. Does anything stand out when you facet the plots?


```{r}
ggplot(districts, aes(x=alg_1, y=alg_2)) +
  geom_point() +
  facet_wrap(~region)
```

Interpretation. There is a strong, positive correlation between higher grades in algebra 1 and algebra 2. If you score higher algebra 1, its postively associated with scoring higher in algebra 2 which makes sense. Some regions have stronger correlation between the two variables than others. Upper Cumberland appears to have no association. 




```{r}
districts
```

8. When creating this bar chart you may have noticed that some districts have missing enrollment values. For how many districts is this the case?


```{r}
districts |> 
 select(system_name, enrollment) |> 
 subset(is.na(enrollment)) |> 
 summarise(total_count = n())
 

```
9. A lot of rows are missing additional values. Which district has the largest number of missing values (across all variables)? Hint: you might want to look at rowwise and c_across to answer this question.


```{r}
districts <- districts |> 
  rowwise() |> # this is a group_by() function by row.
  mutate(count_na = sum(is.na(cur_data())))
  
```

```{r}
districts |> 
  select(count_na, system_name) |> 
  arrange(desc(count_na)) |> 
  head(1)
```
10. What is the mean graduation rate across all districts? What might be wrong with using just the regular mean to assess average graduation rates?


```{r}
districts |> 
  group_by(grad)
  summary(districts$grad)
```

```{r}

```


